\bf Hierarchical Network Structure Promotes Dynamical Robustness

### 2015-07-22 tex/overview.tex
clarify acyclicity of SCC graph

The map from the interaction graph of a network to its SCCs, referred to as $\hier$ in \ref{fig:modsccsym}, results in a decomposition of $G$ into its SCCs. Each node of $\hier (G)$ corresponds to a SCC of $G$. There is an edge from the node corresponding to component $C$ to the node corresponding to component $C'$ if and only if there exists a link from some vertex in $C$ to some vertex in $C'$ in $G$.  Because of the maximality of SCCs, $\hier (G)$ is acyclic for any $G$.

@@

The relationship between $G$ and $\hier(G)$ for all $G$ with a given number of vertices suggests a heuristic method of quantifying the degree of hierarchy of a given graph and thus of the system structure it represents. The most hierarchical system is considered to be the graph corresponding to the total ordering (\refsupp{} and \cite{Cormen2009}), which for three nodes is given in \reffigscc{} (top panel). This graph maximizes the number of links between strongly connected components, which also implies maximizing the number of strongly connected components. The graph edit distance (ED) on a fixed number of vertices from one graph to another is defined as the minimum number of modifications of the first graph in order to transform it into the second \cite{Axenovich2011}. This distance between any given graph and the total ordering thus quantitatively represents how far a graph is from being maximally hierarchical. In this work we take $max(ED) - ED$ to be the definition of hierarchy, where $max(ED)$ is the maximum edit distance for all graphs with a given number of nodes.

@@

\subsection{Most hierarchical network architecture maximizes dynamical robustness}

>>>>

The map from the interaction graph of a network to its SCCs, referred to as $\hier$ in \ref{fig:modsccsym}, results in a decomposition of $G$ into its SCCs. Each node of $\hier (G)$ corresponds to a SCC of $G$. There is an edge from the node corresponding to component $C$ to the node corresponding to component $C'$ if and only if there exists a link from some vertex in $C$ to some vertex in $C'$ in $G$. Note that $\hier (G)$ is acyclic for any $G$ because of the maximality property of SCCs.

@@

The relationship between $G$ and $\hier(G)$ for all $G$ with a given number of nodes suggests a heuristic method of quantifying the degree of hierarchy of a given graph and thus of the system structure it represents. The most hierarchical system is considered to be the graph corresponding to the total ordering (\refsupp{} and \cite{Cormen2009}), which for three nodes is given in \reffigscc{} (top panel). This graph possesses the maximum number of SCCs for any graph with a given number of nodes, $n$, as well as the maximum number, $\binom{n}{2}$, of links between SCCs. The graph edit distance (ED) on a fixed number of nodes from one graph to another is defined as the minimum number of modifications of the first graph in order to transform it into the second \cite{Axenovich2011}. This distance between any given graph and the total ordering thus quantitatively represents how far a graph is from being maximally hierarchical. In this work we take $max(ED) - ED$ to be the definition of hierarchy, where $max(ED)$ is the maximum edit distance for all graphs with a given number of nodes.

@@

\subsection{Most hierarchical network architectures maximize dynamical robustness}
